---
output: github_document
---
<!-- README.md is generated from README.Rmd. Edit README.Rmd and knit. -->
```{r setup, include = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(palmerpenguins)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%",
  fig.align = "center",
  fig.retina = TRUE
)
theme_set(theme_bw())
```
```{r, echo = FALSE}
source("R/colors.R")
```

# twist-color-pal
Thematic Twist Bioscience color palettes for ggplot2
By Patrick Cherry

## Brief Description
The R package `twist_color_pal` provides the `ggplot2` functions `scale_color_twist` and `scale_fill_twist` to automatically and flexibly add Twist Bioscience brand colors to plots.
```{r}
green_ngs_palette();
scales::show_col(green_ngs_palette(), cex_label = 1)
```

## Installation
Use devtools or remotes to install from Twist Bioscience's private github. Twist's Github is private, so use the [Personal access tokens page](https://github.com/settings/tokens) to generate an access token and paste it in between the quotes of ` auth_token = ""` in the `install_github()` command.
```{r, eval = FALSE, echo = TRUE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("Twistbioscience/twist-color-pal", auth_token = "")
```

### Alternative installation
Alternatively, download the package zip and use devtools to install from the local .zip.
```{r, eval = FALSE, echo = TRUE}
if (!require(devtools)) install.packages("devtools")
devtools::install_local(path = "~/Downloads/twist-color-pal.zip")
```

## Examples
### Plots with generic data
```{r}
penguins %>% 
  filter(!is.na(sex)) %>% 
  ggplot(aes(x = sex, y = body_mass_g, color = bill_depth_mm)) +
  geom_jitter(size = 3, width = 0.3) +
  scale_color_twist(discrete = FALSE) +
  labs(title = "Bill depth and body mass by sex",
       y = "Body mass (g)",
       color = "Bill depth (mm)")
```

```{r}
penguins %>%
  filter(!is.na(sex)) %>%
  ggplot(aes(x = species, y = body_mass_g, color = island)) +
  geom_point(size = 2,
              position = position_jitterdodge(jitter.width = 0.4)) +
  scale_color_twist(palette = "purple_genes") +
  labs(title = "Body mass by species and island of residence",
       y = "Body mass (g)",
       color = "Island")
```

```{r}
penguins %>%
  #filter(!is.na(sex)) %>%
  ggplot(aes(x = year, fill = species)) +
  geom_bar(position = position_dodge()) +
  scale_fill_twist(palette = "pink_biopharma") +
  labs(title = "Number of observations for each species by year")
```

## The Palettes
```{r}
names(twist_palettes)
```

```{r}
grays_palette();
scales::show_col(green_ngs_palette(), cex_label = 1)
```

```{r}
blue_oligo_pools_palette();
scales::show_col(blue_oligo_pools_palette(), cex_label = 1)
```

```{r}
purple_genes_palette();
scales::show_col(purple_genes_palette(), cex_label = 1)
```

```{r}
pink_biopharma_palette();
scales::show_col(pink_biopharma_palette(), cex_label = 1)
```

```{r}
orange_variant_library_palette();
scales::show_col(orange_variant_library_palette(), cex_label = 1)
```

```{r}
golds_palette();
scales::show_col(golds_palette(), cex_label = 1)
```

Questions? Concerns? Contact Patrick at pcherry@twistbioscience.com.
Did you use these to make nice plots? Did you present them? Let me know; I'd love to hear. <3
